### 2014-11-13 form.tex
some corrections

An execution is an interleaving of operations and ``snapshots'' of the abstract state
$\epsilon = <o_0, S_0, o_1, S_1, ..., o_n, S_n>$, with
each subsequence $<S_{i-1}, o_i, S_i>$ indicating that operation $o_i$ transforms abstract state $S_{i-1}$ into $S_i$.
An accessor does not mutate state, so it leaves the abstract state unchanged.
We use the shorthand $\s{component}_t$ to indicate the value of $S.$\s{component} immediately after $o_t$ completes and before $o_{t+1}$ commences.

{\it Note:} Symbol $\simeq$ in the following context: $o_t\simeq ...$ means that lefthand {\it operation} ($o_t$) can be equal to the righthand operation. E.g. $\forall k \in K, m \in M o_t\simeq \o{has}_t(m, k) \Leftrightarrow \p{const}_t(m)$ means, that the operation number t ($o_t$) may be $\o{has}(m, k)$ (not the result of such function call) if and only if holds $\p{const}_t(m)$.

@@

  \item ``Erase'' deletes an entry with a given key. If the entry does not exist in the \p{mapping}, it fails. It does not change other mappings if they are not expired.

@@

      x=fail \wedge \p{const}_t(m)\Big)

@@

      \Big(x=\o{put}_t(m, k, v, e) \wedge \big(\exists v'\in V, e'\in \nintset: [k, v', e']\in m.\s{mapping}_{t-1} \wedge e > t \big) \Leftrightarrow\nonumber\\
      x=fail \wedge \p{const}_t(m)\Big)\wedge

@@

      x=fail \wedge \p{const}_t(m)\Big)

>>>>

An execution is an interleaving of operations and ``snapshots'' of the abstract state
$\epsilon = <o_0, S_0, o_1, S_1, ..., o_n, S_n>$, with
each subsequence $<S_{i-1}, o_i, S_i>$ indicating that operation $o_i$ transforms abstract state $S_{i-1}$ into $S_i$.
An accessor does not mutate state, so it leaves the abstract state unchanged, but the state can change due to continuous expiration process.
We use the shorthand $\s{component}_t$ to indicate the value of $S.$\s{component} immediately after $o_t$ completes and before $o_{t+1}$ commences.

{\it Note:} Symbol $\simeq$ in the following context: $o_t\simeq ...$ means that lefthand {\it operation} ($o_t$) can be equal to the righthand operation. E.g. $\forall k \in K, m \in M o_t\simeq \o{has}_t(m, k) \Leftrightarrow \p{const}_t(m)$ means, that the operation number t ($o_t$) may be the $\o{has}(m, k)$ call (not the result of it) if and only if holds $\p{const}_t(m)$. \underline{Attention}: $x=\o{has}_t(m, k)$ has different meaning then $o_t=\o{has}_t(m, k)$.

@@

  \item ``Erase'' deletes an entry with a given key. If the entry does not exist in the \s{mapping}, it fails. It does not change other mappings if they are not expired.

@@

      x=fail \wedge \p{const}_t(m) \wedge o_t=\o{erase}_t(m, k)\Big)

@@

      \Big(x=\o{put}_t(m, k, v, e) \wedge \big(\exists v'\in V, e'\in \nintset: [k, v', e']\in m.\s{mapping}_{t-1} \wedge e > t\big) \Leftrightarrow\nonumber\\
      x=fail \wedge \p{const}_t(m) \wedge o_t = \o{put}_t(m,k,v,e)\Big)\wedge

@@

      x=fail \wedge \p{const}_t(m) \wedge o_t = \o{put}_t(m,k,v,e)\Big)
